Simulating the Lipkin-Meshov-Glikov model on a classical computer

### 2023-05-31 doc/paper.tex
Finished report
Signed-off-by: Gregz9 <gregorkajda@gmail.com>

Here we set the parameters $E_1 = 0$, $E_2 = 4$, $V_{11} = -V_{22} = 3$, and $V_{12} = V_{21} = 0.2$. The non-interacting solutions represent our computational basis. Pertinent to our choice of parameters, at $\lambda \geq \frac{2}{3}$, the lowest eigenstate is dominated by $|1\rangle$ while the upper is $|0\rangle$. At $\lambda = 1$, the $|0\rangle$ mixing of the lowest eigenvalue is 1\%, while for $\lambda \leq \frac{2}{3}$, we have a $|0\rangle$ component of more than 90\%. The character of the eigenvectors has therefore been interchanged when passing $\lambda = \frac{2}{3}$. The value of the parameter $V_{12}$ represents the strength of the coupling between the two states. ([Fys5419, project 1])

@@

\subsection{References}

>>>>

Here we set the parameters $E_1 = 0$, $E_2 = 4$, $V_{11} = -V_{22} = 3$, and $V_{12} = V_{21} = 0.2$. The non-interacting solutions represent our computational basis. Pertinent to our choice of parameters, at $\lambda \geq \frac{2}{3}$, the lowest eigenstate is dominated by $|1\rangle$ while the upper is $|0\rangle$. At $\lambda = 1$, the $|0\rangle$ mixing of the lowest eigenvalue is 1\%, while for $\lambda \leq \frac{2}{3}$, we have a $|0\rangle$ component of more than 90\%. The character of the eigenvectors has therefore been interchanged when passing $\lambda = \frac{2}{3}$. The value of the parameter $V_{12}$ represents the strength of the coupling between the two states. ([Morten, project 1])

@@

\section{References}

[Hundt, 2022] Hundt Robert (2022). Qunatum Computing for Programmers. Cambridge University Press.

[Nielsen, 2021] Nielsen Michael (2021). Qunatum Computation adm Quantum Informantion. Cambridge University Press.

[Physical review C, 2022] Manqoba Q. Hlatshwayo (2022). Simulating excited states og the Lipkin model on a Quantum Computer.

[Basdevant, 2023] Basdevant Jean-Louis (2023). Lectures on Quantum Mechanics With Problems, Exercises and Solutions. Springer Nature Switzerland.

[Scherer, 2019] Scherer Wolfgang (2019). Mathematics of Quantum Computing an Introduction. Springer Nature Switzerland.

[Morten Hjorth-Jensen, 2023] M. Hjorth-Jensen, ”Week 11: VQE and project discussion,” URL: https://github.com/CompPhysics/QuantumComputingMachineLearning/tree/gh-pages/doc/pub/week11 April 2023.

[Morten Hjorth-Jensen, 2023] M. Hjorth-Jensen, ”Week 8: Solving quantum mechanical problems,” URL: https://github.com/CompPhysics/QuantumComputingMachineLearning/tree/gh-pages/doc/pub/week8, March 2023.

[Morten Hjorth-Jensen, 2023] M. Hjorth-Jensen, ”Project 1: Quantum Computing and many-body problems,” URL: https://github.com/CompPhysics/QuantumComputingMachineLearning/blob/gh-pages/doc/Projects/2023/Project1/pdf/Project1.pdf March 2023.
